---
title: "Introduction RAWdataR"
output: rmarkdown::html_vignette
date: "12/16/2019"
author: "Thomas Gredig"
vignette: >
  %\VignetteIndexEntry{Introduction RAWdataR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r, include=FALSE}
library(RAWdataR)
library(knitr)
```

## Inspect Directory

We can find out about `projects` and `users` for a particular directory by inspecting it.

```{r}
path.RAW = raw.getSamplePath()
raw.inspectFolder(path.RAW)
```

One of the instruments is off, let us inspect which file that is:

```{r}
basename(raw.findFiles(path.RAW, instrument='MM160622SI1'))
```

The data filename is missing an instrument. It appears to be a `vsm` data file. The instrument can be added as follows:

```{r}
f = raw.findFiles(path.RAW, instrument='MM160622SI1')
raw.fixInvalidFile(f, instrument='vsm')
```



## Find duplicate RAW data files


```{r}
path.RAW = raw.getSamplePath()
f = raw.findDuplicates(path.RAW,isValid=FALSE)
d1 = data.frame(f=basename(f),md5=raw.getMD5(f),row.names = c())
kable(d1, col.names = c('Duplicated Files','MD5'))
```



This is the list of duplicated files. We can find out what the original file:

```{r}
searchMD5 = d1$md5[!duplicated(d1$md5)]
for(m in searchMD5) {
  print(paste("Duplicates for files with MD5 = ",m))
  f = raw.findFiles(path.RAW, md5=m)
  print(basename(f))
}
```


